---
title: "Milestone_4"
author: "Amy Tan"
date: "10/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(foreign)
library(haven)
library(tidyverse)
```

```{r reading_in_data, echo=FALSE}

#loading datasets in raw-data folder using terminal, and then using read_dta function for Stata files

stanforddata <- read_dta("raw-data/SEDA_county_long_CS_v21.dta")
tract_covariates <- read_dta("raw-data/tract_covariates.dta")

#getting a sense of what variables I want to include in my ggplot

view(stanforddata)
view(tract_covariates)
```

```{r plot, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE}

d <- tract_covariates %>% filter(!is.na(share_white2000)) %>% filter(!is.na(hhinc_mean2000)) %>% filter(state==25)

p<- ggplot(data=d, mapping= aes(x = share_white2000, y=hhinc_mean2000))+
  geom_point(alpha=.2)+
  geom_jitter()+
  geom_smooth()+
  labs(x="Proportion of White People", y="Mean Household Income", title="Share of White People v. Mean Household Income", subtitle="Data from 2000, State of Massachusetts", caption="Source: Opportunity Atlas, https://opportunityinsights.org/data/")
p


